SVG: The Paper

### 2022-04-25 Analysis/index.Rmd
post weights figure

@@

plt_b + plt_c + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom',
        legend.direction = 'horizontal')
ggsave("../Figures/qjep_preds.png", width = 9, height = 4)
```

>>>>

ggsave("../Figures/qjep_preds.png", width = 8, height = 4)

@@

plt_b + plt_c + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom',
        legend.direction = 'horizontal')

```
